---
title: "Content & Deliverables"
format: html
editor: visual
---

# 1) Community Project - Disaster Response Mapping

## 

# 2) Capstone Project - Fuel type Mapping

## Preliminary Fuel Type Map

```{r leaflet, include = FALSE}
library(leaflet)
library(terra)

Pre_FTM <- rast("C:/Users/kelvin55.stu/OneDrive - UBC/Documents/GitHub/E-Portfolio/E_Portfolio/Preliminary_FTM.tif")

pal <- colorFactor(
  palette = c(
    "#00FF00", # Broadleaf (Bright Green)
    "#008000", # Conifer (Dark Green)
    "#FF0000", # Shrub (Red)
    "#E69F00", # Grass (Orange/Gold)
    "#808080", # Bare Soil (Gray)
    "#FFFFFF", # Urban (White/Blank)
    "#0000FF"  # Water (Blue)
  ),
  domain = values(Pre_FTM),
  na.color = "transparent"
)

Lea_01 <- leaflet(width = 600, height = 600) %>%
  addProviderTiles("Esri.WorldImagery") %>%
  addRasterImage(Pre_FTM, colors = pal, opacity = 0.8, maxBytes = 10 * 1024 * 1024) %>%
  addLegend(pal = pal, values = values(Pre_FTM), opacity = 0.8, title = "Fuel Type") %>%
  addScaleBar(position = "bottomleft")

```

```{r map, echo=FALSE}
Lea_01
```

## Biophysical Inputs: Biomass & Dryness indices

## Refined Fuel Model Map

# 3) Graduate Coursework Project - City Suitability Mapping

## 

This is a sample page where you can archive project deliverables. Every header you use will correspond to a tab in the legend - shown on the right-hand side of your screen ("On this page").

If you've produced any GIS layers for your 599 project, this may be a good place to share them as interactive maps through leaflet. Alternatively, you can upload high-res figures showing correlations, box-plots, etc. from your report here, and provide a brief overview of key project results. If you have written some useful functions, you may also want to share those here to demonstrate proficiency in particular coding languages or synergies between notable coding packages.

## Leaflet

Sample leaflet - for detailed leaflet instructions, visit the FCOR 599 workshop archive page [here](https://ubc-mgem-fcor599.github.io/FCOR-599-Workshops/Interactive_Maps/leaflet.html).

```{r leaflet, include = FALSE}
library(dplyr); library(leaflet)

m <- leaflet() %>%
  addProviderTiles("Esri.WorldImagery") %>%
  addScaleBar(position = c("bottomleft")) %>%
  setView(-123.1207, 49.2827, zoom = 11)

```

```{r map, echo=FALSE}
m
```

## Code Snippets

Sample code snippet. Notice that you can provide a toggle to switch between coding languages - this is referred to as a 'tabset' in quarto. It is good practice to try and convert your R code to python, and vice-versa to demonstrate coding proficiency. For example, let's showcase a function for calculating NDVI in R and Python.

::: {.panel-tabset group="language"}
## R

``` (.r)
calc_ndvi <- function(nir, red){
  ndvi <- (nir-red)/(nir+red)
  return(ndvi)
}
```

(Assuming *nir* and *red* are terra rast objects)

## Python

``` (.python)
def calc_ndvi(nir, red): 
  ndvi = (nir - red)/(nir + red)
  return(ndvi)
```

(Assuming *nir* and *red* are numpy arrays)
:::

## External links

You can also provide a frame linking to external websites. For example, here is a Google Earth Engine application I developed - which I embedded in this webpage using the code below:

```{code}

<iframe width="900" height="700"
src="https://ee-melserramon.projects.earthengine.app/view/thermal-analysis-tool">
</iframe>
```

The full-screen GEE application is available [here](https://ee-melserramon.projects.earthengine.app/view/thermal-analysis-tool) in case you're interested.

(To use the GEE tool, navigate to any city you'd like, hit apply filters, and click anywhere on the map to retrieve a time-series of Landsat surface temperature observations for that point. Areas where the maximum temp exceeded 35 degrees Celsius in your date-range are highlighted in red.)

```{=html}
<iframe width="900" height="700" src="https://ee-melserramon.projects.earthengine.app/view/thermal-analysis-tool"></iframe>
```
